The search for long-period transiting planets in the \kepler\ light curves

### 2015-03-08 document/ms.tex
more words and hackin

Many of the most dynamically interesting planets will be on orbits longer
than the baseline of existing transit surveys (\kepler, \KT).
Future surveys (\TESS, PLATO?) will have such a short continuous coverage that
even habitable zone planets around M-dwarfs will only present a single transit
signal.
Searches for these transiting planets are plagued by false
signals---especially when pushed to low signal-to-noise---and statistical
studies of their population are complicated by weak constraints on the
physical parameters of the system and high rates of false positives.
We develop and present a computationally expensive but tractable method of
searching for single transits using supervised classification methods from
the machine learning literature.
For each month of photometry, we train a random forest classifier on a large
number of simulated signals injected into the photometry of the same star at
different times.
Then, the model's prediction as a function of transit time is evaluated and
times above a threshold probability---chosen for each star to yield a sample
with $\sim99$~percent purity---are given as candidate transits.
Each candidate must then pass a final round of vetting including BLAH BLAH
BLAH.
Applied to every light curve in the \kepler\ archive this method yields a
list of XXXX long-period transiting planet candidates.
Using an informative prior on their eccentricities, we derive weak constraints
on the orbital periods of the candidates and demonstrate that this puts an
upper limit of ZZZZ on the occurrence rate of these planets.

@@

Hi \citep{kois}.

>>>>

Many of the most dynamically interesting planets will be on orbits longer
than the baseline of existing transit surveys (\kepler, \KT).
Future surveys (\tess, PLATO?) will have such a short continuous coverage that
even habitable zone planets around M-dwarfs will only present a single transit
signal.
Searches for these transiting planets are plagued by false
signals---especially when pushed to low signal-to-noise---and statistical
studies of their population are complicated by weak constraints on the
physical parameters of the system and high rates of false positives.
We develop and present a computationally expensive but tractable method of
searching for single transits using supervised classification methods from
the machine learning literature.
For each month of photometry, we train a random forest classifier on a large
number of simulated signals injected into the photometry of the same star at
different times.
Then, the model's prediction as a function of transit time is evaluated and
times above a threshold probability---chosen for each star to yield a sample
with $\sim99$~percent purity---are given as candidate transits.
Each candidate must then pass a final round of vetting including BLAH BLAH
BLAH.
Applied to every light curve in the \kepler\ archive this method yields a
list of XXXX long-period transiting planet candidates.
Using an informative prior on their eccentricities, we derive weak constraints
on the orbital periods of the candidates and demonstrate that this puts an
upper limit of ZZZZ on the occurrence rate of these planets.

@@

\begin{itemize}

\item Description of the physical significance of these planets

\item Discussion of previous attempts (papers by Gaudi, Yee, Payne, Bakos,
\etc).

\item Comparison of method to filtering methods and an argument for why
supervised classification should be more robust to false alarms given a large
enough training set

\end{itemize}

\citep{kois}

\section{Dataset \& pre-processing}

\section{Training the classifier}

The positive examples of planet transits in the training set is generated by
randomly selecting 121 cadence-long chunks of photometry and multiplying in a
transit model generated by sampling the physical parameters from SOME
DISTRIBUTIONS listed in SOME TABLE.
The negative examples are randomly chosen chunks of the same length.
When the model is to be used to search for transits in a specific month of
data, the examples from that month are removed from the training set and the
remaining examples are used.

Practically, the features used as input to the classifier are just the flux
values themselves normalized to unit median flux.

\section{Search}

\section{Transit candidates \& their orbits}

\section{Detection efficiency \& false alarms}

\section{Astrophysical false positives}

\section{The population of long-period transiting planets}

\section{Discussion}
